# Data visualisation

```{r tidyverse ,include=FALSE}
library(tidyverse)
```

## 3.2.4 Exercises {-}

1. Run ggplot(data = mpg). What do you see?

```{r}
ggplot(data = mpg)
```

> empty graph, because we don't set the aesthetic mapping for plot.

2. How many rows are in mpg? How many columns?

```{r, collapse=TRUE}
dim(mpg)
```

> rows: `r dim(mpg)[1]`, columns: `r dim(mpg)[2]`

3. What does the drv variable describe? Read the help for ?mpg to find out. 

```{r}
?mpg
```

> drv: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

4. Make a scatterplot of hwy vs cyl.

```{r}
ggplot(mpg) + 
  geom_point(aes(x = hwy, y = cyl))
```

5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

```{r}
ggplot(mpg) +
  geom_point(aes(class, drv))
```

## 3.3.1 Exercises {-}

1. What’s gone wrong with this code? Why are the points not blue?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

> Need to put color attribute outside the aes()   
> Because the color argument was set within aes(), not geom_point()

2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?

```{r, collapse=TRUE}
str(mpg)
```

> Categorical: manufacturer, model, trans, drv, fl, class   
> Continuous: displ, cyl, cty, hwy

3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

**color:**

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy, color = cty))
```

**shape:**

```{r, error=TRUE, collapse=TRUE, fig.show='hide'}
ggplot(mpg) + 
  geom_point(aes(displ, hwy, shape = cty))
```

**size:**

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy, size = cty))
```

4. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy, color = manufacturer, size = manufacturer))
```

5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

>  To modify the width of the border   

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy, color = class, stroke = 5))
```

6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy, color = displ < 5))
```














